Reply To Examiners

### 2014-04-01 answer_thesis_examiner/answer_document.tex
auto

>>>>

In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...

The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
He went on to ask: ``What kind of eror will it cause?''.
To this the answer is that the model inherently suffers from loss of dimension
  where the full data is multi-dimensional and the proposed models are scalar.

Besides these main points, the chapter is updated to increase its pursuasive power.
For example: the sentence in line 1, page 133, section 6.3 is removed.
Or a list of achievements has been included in this chapter.

\subsubsection*{9. Appendix}

While the conference papers have been published and the journal paper submitted,
  their copies have been removed from this section.
